A Reduced Order Model for Porous Media Flows: Coupling Linear Regression with Principal Component Analysis (PCA) using High-Order Singular Value Decomposition (HOSVD) in Upscaling Calculations for Permeability in Reservoir Simulations

### 2018-12-03 Papers/AppliedMaths2018/Resubmission/Stochastic_Upscaling_UK_AMM_2018b.tex
files to be modified in the next 250min

\medskip
Finally, $\mathbf{K}\left(\mathbf{r}\right)$, the focus of this work, is the absolute permeability tensor of the porous medium and it is a function of the vector position $\mathbf{r}$. $\mathbf{K}$ is prescribed in the system of governing conservative equations, \ie it is an indepedent input variable. Since $\mathbf{K}$ is a petrophysical rock property that varies spatially, it cannot be determined at every spatial coordinate. And, even if this information is available at every spatial coordinate, it would require immense computer resources to process during flow simulations. This is the reason upscaling is required for processing permeability variables. Upscaling can be performed from the continuum scale, across the micro scale ($mm$), local scale and meso scale ($m$) to the field scale ($km$)\cite{ECMI_2004}. The upscaling discussed here is from the micro scale also known as the Darcy scale.

>>>>

\medskip
Finally, $\mathbf{K}\left(\mathbf{r}\right)$, the focus of this work, is prescribed in the system of governing conservative equations, \ie it is an independent input variable. Since $\mathbf{K}$ is a petrophysical property of geological formations that varies spatially, it cannot be determined at every grid point (\ie spatial coordinate). And, even if this information is available at every spatial coordinate, it would require immense computer resources to process during flow simulations. This is the reason upscaling is required for processing permeability spatial variability. Upscaling can be performed from the continuum scale, across the micro-scale ($mm$), local- and meso-scale ($m$) to field-scale ($km$)\cite{ECMI_2004}. The upscaling discussed here is for micro-scale, also known as the Darcy scale.
